ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-11-14 pyked.tex
changes to paper and class for submission
IJCK submission system doesn't like minted, so for submission we have
to use the "frozencache" option.
made various easy changes for second round of reviewer comments

% !TEX option = -shell-escape
%% comment out the above line before submitting
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This work is licensed under the Creative Commons Attribution 4.0
% International License. To view a copy of this license, visit
% http://creativecommons.org/licenses/by/4.0/.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{ijck}

@@

@@

Nonetheless, databases of fundamental combustion experiments
have proved quite useful. For instance, Olm and colleagues used their
ReSpecTh-based database to quantify the performance of literature
hydrogen~\autocite{Olm:2014gn} and syngas~\autocite{Olm:2015ch} kinetic models,
and more recently develop improved models for hydrogen\slash
syngas~\autocite{Varga:2016gj}, methanol\slash formaldehyde~\autocite{Olm:2017a},
and ethanol~\autocite{Olm:2016et}. In all five cases, they converted numerous
experimental datasets from the literature into the ReSpecTh standard.
Their database currently contains \num{93240} experimental data points in 1376
ReSpecTh XML files~\autocite{respecth}.

@@

The second section of the file encodes the experimental data as a sequence of mappings. The
top-level key for the sequence is called \yabox|datapoints|. For the current version of the \ck{}
schema, only autoignition delay experiments are supported. The following information os required in
each element of the sequence:
%
\begin{itemize}
    \item \yabox|temperature| (required, sequence): The temperature of the
    experiment, with units and optionally uncertainty
    \item \yabox|ignition-delay| (required, sequence): The ignition delay of the
    experiment, with units and optionally uncertainty
    \item \yabox|pressure| (required, sequence): The pressure of the experiment,
    with units and optionally uncertainty
    \item \yabox|first-stage-ignition-delay| (optional, sequence): If two stages of ignition are
    present in the experiment, this is the length of the first stage of ignition, and the
    \yabox|ignition-delay| is then the overall ignition delay
    \item \yabox|equivalence-ratio| (optional, float): The value of the equivalence ratio
    \item \yabox|composition| (required, mapping): The composition of the
    mixture in the experiment, described via a nested mapping with the fields:
    \begin{itemize}
        \item \yabox|kind| (required, string): one of \yabox|mole fraction|, \yabox|mole percent|, or \yabox|mass fraction|
        \item \yabox|species|: sequence of mappings, with the fields:
        \begin{itemize}
            \item \yabox|species-name| (required, string): The name of the species
            \item \yabox|amount| (required, sequence): The mole fraction or percent, or the mass fraction, optionally with uncertainty
            \item \yabox|InChI|, \yabox|SMILES|, or \yabox|atomic-composition|
            (required, string or sequence): The InChI
            or SMILES string representing the molecule, or its atomic
            composition as a sequence
        \end{itemize}
    \end{itemize}
    \item \yabox|ignition-type| (required, mapping): The method used to detect
    ignition in the experiments. The required fields are
    \begin{itemize}
        \item \yabox|type| (required, string): How ignition delay was
        measured; one of \yabox|d/dt max| (indicates the ignition point was
        found at the maximum of the time derivative of the \yabox|target|),
        \yabox|max| or \yabox|min| (indicates the ignition point was at the
        maximum or minimum of the \yabox|target|), \yabox|1/2 max| (
        indicates the half-maximum point of \yabox|target|), or \yabox|d/dt max extrapolated|
        (indicates the maximum slope of the target extrapolated to the baseline)
        \item \yabox|target| (required, string): The target for the ignition
        \yabox|type| measurement; one of \yabox|temperature|, \yabox|pressure|,
        \yabox|OH|, \yabox|OH*|, \yabox|CH|, or \yabox|CH*|
    \end{itemize}
\end{itemize}

@@

The \pybox|write_file()| method writes a new \ck{} YAML file based on the instance attributes
of the class, while \pybox|convert_to_ReSpecTh()| converts the \pybox|ChemKED|
instance to a ReSpecTh XML file. In the latter case, some information may be lost or the conversion
may not be possible, as \ck{} files support some data that ReSpecTh files do not support. We note
that the reverse is also true: not all ReSpecTh files may be converted to \ck{} files because not
all of the data that can be stored in a ReSpecTh format is (currently) supported by the \ck{} format.

>>>>

%% !TEX option = -shell-escape
%% comment out the above line before submitting
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This work is licensed under the Creative Commons Attribution 4.0
% International License. To view a copy of this license, visit
% http://creativecommons.org/licenses/by/4.0/.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{ijck}

@@

% For the version with changes, use these four commands
% *** Be very precise and careful about including whitespace and punctuation in your edits ***
\usepackage[normalem]{ulem}
\newcommand{\addone}[1]{{\sloppy\textcolor{teal}{\uline{#1}}}}  % add
\newcommand{\deleteone}[1]{\sloppy\textcolor{teal}{\sout{#1}}}    % delete
\newcommand{\addtwo}[1]{{\sloppy\textcolor{red}{\uline{#1}}}}  % add
\newcommand{\deletetwo}[1]{\sloppy\textcolor{red}{\sout{#1}}}    % delete

@@

Nonetheless, databases of fundamental combustion experiments
have proved quite useful. For instance, Olm and colleagues used their
ReSpecTh-based database to quantify the performance of literature
hydrogen~\autocite{Olm:2014gn} and syngas~\autocite{Olm:2015ch} kinetic models,
and more recently develop improved models for \addtwo{hydrogen~\autocite{Varga:2015hy}},
hydrogen\slash syngas~\autocite{Varga:2016gj},
methanol\slash formaldehyde~\autocite{Olm:2017a},
and ethanol~\autocite{Olm:2016et}. In all \deletetwo{five}~\addtwo{six} cases, they converted numerous
experimental datasets from the literature into the ReSpecTh standard.
Their database currently contains \deletetwo{\num{93240}}~\addtwo{\num{93326}}
experimental data points in \deletetwo{1376}~\addtwo{1396}
ReSpecTh XML files~\autocite{respecth}.

@@

The second section of the file encodes the experimental data as a sequence of mappings. The
top-level key for the sequence is called \yabox|datapoints|. For the current version of the \ck{}
schema, only autoignition delay experiments are supported. The following information
\deleteone{os}~\addone{is} required in each element of the sequence:
%
\begin{itemize}
    \item \yabox|temperature| (required, sequence): The temperature of the
    experiment, with units and optionally uncertainty
    \item \yabox|ignition-delay| (required, sequence): The ignition delay of the
    experiment, with units and optionally uncertainty
    \item \yabox|pressure| (required, sequence): The pressure of the experiment,
    with units and optionally uncertainty
    \item \yabox|first-stage-ignition-delay| (optional, sequence): If two stages of ignition are
    present in the experiment, this is the length of the first stage of ignition, and the
    \yabox|ignition-delay| is then the overall ignition delay
    \item \yabox|equivalence-ratio| (optional, float): The value of the equivalence ratio
    \item \yabox|composition| (required, mapping): The composition of the
    mixture in the experiment, described via a nested mapping with the fields:
    \begin{itemize}
        \item \yabox|kind| (required, string): one of \yabox|mole fraction|, \yabox|mole percent|, or \yabox|mass fraction|
        \item \yabox|species|: sequence of mappings, with the fields:
        \begin{itemize}
            \item \yabox|species-name| (required, string): The name of the species
            \item \yabox|amount| (required, sequence): The mole fraction or percent, or the mass fraction, optionally with uncertainty
            \item \yabox|InChI|, \yabox|SMILES|, or \yabox|atomic-composition|
            (required, string or sequence): The InChI
            or SMILES string representing the molecule, or its atomic
            composition as a sequence
        \end{itemize}
    \end{itemize}
    \item \yabox|ignition-type| (required, mapping): The method used to detect
    ignition in the experiments. The required fields are
    \begin{itemize}
        \item \yabox|type| (required, string): How ignition delay was
        measured; one of \yabox|d/dt max| (indicates the ignition point was
        found at the maximum of the time derivative of the \yabox|target|),
        \yabox|max| or \yabox|min| (indicates the ignition point was at the
        maximum or minimum of the \yabox|target|), \yabox|1/2 max| (
        indicates the half-maximum point of \yabox|target|), or \yabox|d/dt max extrapolated|
        (indicates the maximum slope of the target extrapolated to the baseline)
        \item \yabox|target| (required, string): The target for the ignition
        \yabox|type| measurement; one of \yabox|temperature|, \yabox|pressure|,
        \yabox|OH|, \yabox|OH*|, \yabox|CH|, or \yabox|CH*|
    \end{itemize}
\end{itemize}

@@

The \pybox|write_file()| method writes a new \ck{} YAML file based on the instance attributes
of the class, while \pybox|convert_to_ReSpecTh()| converts the \pybox|ChemKED|
instance to a ReSpecTh XML file. In the latter case, some information may be lost or the conversion
may not be possible, as \ck{} files support some data that ReSpecTh files do not support. We note
that the reverse is also true: not all ReSpecTh files may be
\addtwo{equivalently} converted to \ck{} files because not
all of the data that can be stored in a ReSpecTh format is (currently) supported by the \ck{} format.
